\documentclass[12pt]{article}

\usepackage{amssymb,amsmath,amsthm}
\usepackage{graphicx} % Package for including figures
%\usepackage{psfrag,color}
\usepackage[utf8]{inputenc}
\usepackage{longtable}

\title{HW2 Data Report for Math/CS 471}
\author{Xiaomeng Li}
\date{09/16/2017}   % Activate to display a given date or no date


\begin{document}
\maketitle

\begin{abstract}
This is the HW2 report. This report is made all through LaTeX.
\end{abstract}

\section{Question 1}
We run the script and see the output. The iteration is ten times.

\section{Question 2}
Please see the newtonS.f90.Template file. The do-while loop is used
for approximating the absolute error.

\section{Question 3}
In newtonS.f90.Template file, I add linear and quadratic convergence
right after the x output. So for every iteration there should be a
total of 6 outputs.

\section{Question 4}
\subsection{Convergence}
The first number is linear convergence and the second is quadratic
convergence.  
Rate of convergence for 'x' is 0.5000000000000000E+00 and
0.5000000000000000E+00.
Rate of convergence for 'x*x' is 0.5000000000000000E+00 and 
0.1407374883553280E+15. 
Rate of convergence for 'sin(x)+cos(x*x)' is 0.1633240749027686E-04 and
0.7677507053309917E+00.
The results are read from the file when the iteration reaches maximum.

\subsection{Convergence discussion}
$f'(x)$ is ('1.d0', '2.d0*x', 'cos(x)-2.d0*x*sin(x*x)'). 
For the first one, when x comes closer to its root, there should not
be very big change happening since $f'(x)$ is already a
constant. However, when it comes to the second one, it is difficult to
determine convergence since x still exists in the equation. The third
is better since they are cos() and sin(), which is more possible to give a
final rate of convergence I think when it comes to quadratic
convergence. The data also proves this quadratic convergence when it
reaches fifth and sixth iteration in case three.

\subsection{Modified Newton’s method discussion}
I think I will implement Modified Newton’s method on case two since
the multiplicity m of the root is known in advance (I know what $f'(x)$
is as soon as I have a x). $-$$m\times($f'(x)$/$f(x)$)$ = $x_{n+1}$ $-$ $x_{n}$. So I will just modify newtonS.f90.Template file.
\section{Question 5}
$>>$ is actally more useful.
\section{Question 6}
One good method writing double slashes at the end of each output data row has
not come up though.
\section {Tabulated Data}
Explanation: the first character is the case ( 'x', 'x*x' ,
'sin(x)+cos(x*x)'). The second number is the iteration number. The
third one is x value, the forth one is dx, the fifth one is linear
convergence and the sixth one is quadratic convergence.
\subsection{Convergence Results Table}
 
\begin{centering}
\begin{longtable}[h]
 
\hline
 \hline
\input{tmp2modify.tex}  
 \hline
\hline

\end{longtable}
\end{centering}

\end{document}



